Reference model in feature selection problems \vspace{.1in}

### 2019-05-24 paper/ref_approach.tex
fixed bootstrap results with 1000 simulations for projpred

\hypertarget{projection}{%
\subsection{Benefits of the reference model: an example with the projection predictive approach}\label{projection}}
\begin{itemize}
\item correct bootstrap results for projpred --> 1000 bootstrap samples 
\item thus correct the comment on the table and on the barplot!!!!
\end{itemize}

@@

\cite{paper:bodyfat} report the results using the stepwise backward elimination with a significance level of 0.157 with AIC selection fixing abdomen and height to be always included in the model. We implement the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search, the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}. In order to automatise the procedure, we select the submodel size as the smallest which has an elpd score higher than the reference model with probability 0.05. Figure \ref{fig:inclusion_frequencies} shows the bootstrap inclusions frequencies combining the results from \cite{paper:bodyfat} for the stepwise backward elimination and our experiments for the projection. The projection predictive approach has only two variables with inclusion frequencies above 50 (abdomen is the only included always), while the stepwise regression has seven features, of which abdomen and height are fixed. Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}. The first five selected models have a cumulative frequency of 74\% with projpred, whereas with the stepwise regression only of 11.5\%. In addition to that we note that the size of the selected model is much smaller when using projpred.

@@

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l||l|r||l|r}
  \hline
M & projpred & Freq & steplm & Freq  \\ 
  \hline
1 & abdomen, weight & 37 & abdomen, height, wrist, age, chest, biceps & 32 \\
2 & abdomen, wrist & 10 & abdomen, height, wrist, age, neck, forearm, thigh, hip & 29 \\
3 & abdomen, height & 10 & abdomen, height, wrist, age, forearm, chest & 19 \\
4 & abdomen, height, wrist & 9 & abdomen, height, wrist, age, neck, forearm, chest & 19 \\
5 & abdomen, weight, wrist & 8 & abdomen, height, wrist, age, neck, forearm, chest, thigh, hip & 19 \\
6 & abdomen, chest, height, wrist & 3 & abdomen, height, wrist, age, neck, chest, biceps & 18 \\
7 & abdomen, height, neck, wrist & 2 & abdomen, height, wrist, age, neck, thigh, biceps, hip & 16 \\
8 & abdomen, age, wrist & 2 & abdomen, height, wrist, age, neck, forearm & 15 \\
9 & abdomen, age, height, neck, thigh, wrist & 2 & abdomen, height, wrist, age, neck, biceps & 15 \\
10 & abdomen, chest & 1 & abdomen, height, wrist, age, beck, forearm, chest, biceps & 14 \\
   \hline
\end{tabular}
\caption{Bootstrap model selection frequencies after 1000 bootstrap samples.}
\label{tab:model_frequencies}
\end{table}

>>>>

\hypertarget{projection}{%
\subsection{Benefits of the reference model: an example with the projection predictive approach}\label{projection}}

@@

\cite{paper:bodyfat} report the results using the stepwise backward elimination with a significance level of 0.157 with AIC selection fixing abdomen and height to be always included in the model. We implement the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search, the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}. In order to automatise the procedure, we select the submodel size as the smallest which has an elpd score higher than the reference model with probability 0.05. Figure \ref{fig:inclusion_frequencies} shows the bootstrap inclusions frequencies combining the results from \cite{paper:bodyfat} for the stepwise backward elimination and our experiments for the projection. The projection predictive approach has only two variables with inclusion frequencies above 50 (abdomen is the only included always), the third most included is `wrist' at 49.5 and the fourth is `height' at 27.8, while the stepwise regression has seven features above 50, of which abdomen and height are fixed. Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}. The first five selected models have a cumulative frequency of almost 70\% with projpred, whereas with the stepwise regression only of 11.8\%. In addition to that we note that the size of the selected model is much smaller when using projpred.

@@

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l||l|r||l|r}
  \hline
M & projpred & Freq (\%) & steplm & Freq (\%)  \\ 
  \hline
1 & abdomen, weight & 34.2 & abdomen, height, wrist, age, chest, biceps & 3.2 \\
2 & abdomen, wrist & 13.3 & abdomen, height, wrist, age, neck, forearm, thigh, hip & 2.9 \\
3 & abdomen, weight, wrist & 7.6 & abdomen, height, wrist, age, forearm, chest & 1.9 \\
4 & abdomen, height & 7.4 & abdomen, height, wrist, age, neck, forearm, chest & 1.9 \\
5 & abdomen, height, wrist & 6.7 & abdomen, height, wrist, age, neck, forearm, chest, thigh, hip & 1.9 \\
6 & abdomen, age, wrist & 2.9 & abdomen, height, wrist, age, neck, chest, biceps & 1.8 \\
7 & abdomen, height, neck & 2.2 & abdomen, height, wrist, age, neck, thigh, biceps, hip & 1.6 \\
8 & abdomen, age, height, wrist & 1.2 & abdomen, height, wrist, age, neck, forearm & 1.5 \\
9 & abdomen, weight, thigh & 1.1 & abdomen, height, wrist, age, neck, biceps & 1.5 \\
10 & abdomen, weight, neck & 1.0 & abdomen, height, wrist, age, beck, forearm, chest, biceps & 1.4 \\
   \hline
\end{tabular}
\caption{Bootstrap model selection frequencies after 1000 bootstrap samples.}
\label{tab:model_frequencies}
\end{table}
